%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{3.6cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{David}{Eklov}
\address{290 South Castanya Way}{94028 Menlo Park, CA}
\phone[mobile]{+1~(512)~423~9232}
\email{david.eklov@gmail.com}


% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

Software architect with deep experience in many areas. Have worked on bootloaders, operating system kernels, hardware simulators and compilers all the way up to cloud devops, microservice architectures, data pipelines, statistical models and machine learning.

\section{Professional Experience}
\cventry{Mar, 2018--present}{Chief Scientist}{unitQ}{San Mateo, CA}{}{
Architected and lead the engineering teams that built unitQ’s first product, the
unitQ Monitor. The Monitor ingests and analyzes public and proprietary user
feedback (e.g., support emails, tweets, app reviews, etc.) and identifies bugs in
our customers’ software services reported by their users.
\newline
\newline
\textbf{Highlights}:
\begin{itemize}
\item Build and lead two distributed engineering teams
\begin{itemize}
\item Frontend/Backend - 7 engineers
\item Data Science/Machine Learning - 5 engineers
\end{itemize}
\item Architected and lead the implementation of
\begin{itemize}
\item Kubernetes based backend with 15+ micro services
\item Data pipeline with several state-of-the-art ML/NLP models
\item Highly available data crawling infrastructure for 10+ data different sources
\item CI/CD pipeline using CircleCI and Helm
\item Tooling for training ML models on Google AI platform
\end{itemize}
\item Lead the development of several ML/NLP models
\begin{itemize}
\item Various BERT based text classification models
\item BERT + human-in-the-loop based text clustering algorithm
\end{itemize}
\item Designed tools, defined and ran processes to manage 10+ humans in the loop
\item Helped raise \$11M series A lead by Gradient Ventures (Google's AI fund)
\end{itemize}
\ \newline
\textbf{Technologies Used}: Kubernetes, Elasticsearch, DynamoDB, Aurora, Kinesis, Terraform, Google AI Platform, Tensorflow 2.0, Keras, Huggingface Transformers, scikit-learn, Scala, Python, Java.
}

\cventry{Oct, 2018 -- Mar, 2018}{Performance Architect}{Samsung}{Austin, TX}{}{
\begin{itemize}
\item Designed and implemented a high-performance, full-system, functional, multicore
simulator for the ARM architecture capable of booting unmodified Linux and
Android software stacks. The simulator was written in C++. I did most of the
initial implementation work including: memory model, interrupt routing, DMA
engine, various device models such as interrupt, block and network device controllers,
and the internal threading model for enabling non-blocking I/O. I also did the Linux
and Android bring-up.
\item Worked on source-to-source compiler, written in Scala, for compiling a pseudo code
description of the ARM instruction set into optimized C++ code used to simulate
instructions in high-performance, multicore CPU model.
\item Developed and maintained user-space tools and Linux drivers for proprietary perfor-
mance monitoring units. Helped configure and tune the kernel and system software
for other teams working with Linux and Android workloads.
\end{itemize}
}

\cventry{Aug, 2007 -- Dec, 2008}{Software Engineer}{Acumem}{Uppsala, Sweden}{}{
Acumem was founded in 2006 to develop optimization tools for multithreaded programs
using statistical analysis of memory access patterns. I joined the company in an early
stage and worked on the core cache modeling technology for Acumem’s first software
release. Acumem was acquired by Rough Wave Software in 2010.
}

\cventry{Jan, 2007 -- Jun, 2007}{Intern, Software Engineer}{Vmware}{Palo Alto, CA}{}{
Proposed, implemented and evaluated a storage IO bandwidth manager for the ESX
server.
}

\cventry{Jan, 2006 -- Jun, 2006}{Intern, Quality Assurance}{Vmware}{Palo Alto, CA}{}{
Implemented testing framework to test the operation system kernel of the ESX server.
}

\section{Education}
\cventry{Sep, 2007 -- Oct, 2012}{Ph.D.}{Uppsala University}{Uppsala, Sweden}{}{
Computer Architecture\newline
Developed novel methods for software performance analysis on multicore architectures.
The methods provide quantitative data of how applications’ utilize resources in the
memory hierarchy, such as cache capacities and bandwidths. This data has been used
to predict and explain how applications scale with increasing core counts, to determine
how the performance of applications is impacted by resource sharing and to guide
compiler optimizations.
}

\cventry{Sep, 2001 -- Dec, 2006}{M.Sc.}{Chalmers University of Technology}{Gothenburg, Sweden}{}{
Electrical Engineering and Applied Mathematics
}

\section{Experience}
\subsection{Vocational}
\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.\newline{}%
Detailed achievements:%
\begin{itemize}%
\item Achievement 1;
\item Achievement 2, with sub-achievements:
  \begin{itemize}%
  \item Sub-achievement (a);
  \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
    \begin{itemize}
    \item Sub-sub-achievement i;
    \item Sub-sub-achievement ii;
    \item Sub-sub-achievement iii;
    \end{itemize}
  \item Sub-achievement (c);
  \end{itemize}
\item Achievement 3.
\end{itemize}}
\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
\subsection{Miscellaneous}
\cventry{year--year}{Job title}{Employer}{City}{}{Description}

\section{Languages}
\cvitemwithcomment{Language 1}{Skill level}{Comment}
\cvitemwithcomment{Language 2}{Skill level}{Comment}
\cvitemwithcomment{Language 3}{Skill level}{Comment}

\section{Computer skills}
\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Interests}
\cvitem{hobby 1}{Description}
\cvitem{hobby 2}{Description}
\cvitem{hobby 3}{Description}

\section{Extra 1}
\cvlistitem{Item 1}
\cvlistitem{Item 2}
\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}

\section{Extra 2}
\cvlistdoubleitem{Item 1}{Item 4}
\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

\section{References}
\begin{cvcolumns}
  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template.tex'.
